Characteristic polynomials of p-adic matrices

### 2017-01-30 charpoly/charpoly.tex
Move 4.1 to Section 2

\begin{prop}
Let $A$ be the subring of $K[X]$ consisting of polynomials $P$ for
which $P(M) \in M_n(\OK)$. Then $d \chi_M \big(M_n(\OK)\big)$ 
(considered as a submodule of $K[X]/\chi_M(X)$) is stable by 
multiplication by the elements of $A$.
\end{prop}
\begin{proof}
\todo{The image is generated by the entries of $C = \com(X-M)$
and we have $P(M) \cdot C \equiv  P(X) \cdot C \pmod{\chi_M(X)}$.}
\end{proof}

>>>>

\begin{prop}
Let $A$ be the subring of $K[X]$ consisting of polynomials $P$ for
which $P(M) \in M_n(\OK)$. Then $d \chi_M \big(M_n(\OK)\big)$ 
(considered as a submodule of $K[X]/\chi_M(X)$) is stable by 
multiplication by the elements of $A$.
\end{prop}
\begin{proof}
\todo{The image is generated by the entries of $C = \com(X-M)$
and we have $P(M) \cdot C \equiv  P(X) \cdot C \pmod{\chi_M(X)}$ since the entries of $P(X) \cdot C$
are linear combinations with integer coefficients of the entries of $C$.  $C*(X-M) = \chi(M)$ (since matrix * comatrix is determinant).}
\end{proof}
